Supporting Information

### 2021-12-10 Asymptomatic_LSR_Supplement_noPrisma_yesROB_HI.Rmd
update

#censor until 5296 (31 Jan) plus the published versions of preprints
pub_preprints <- c(5565, 6219, 6685, 7030, 7465, 8249, 9442, 9484) #published version of preprints before 31 Jan
rob_records <- rob_records %>%
  filter(record_id %in%  pub_preprints | record_id <= 5296)

>>>>

#censor until 5296 (31 Jan) plus the published versions of preprints
# pub_preprints <- c(5565, 6219, 6685, 7030, 7465, 8249, 9442, 9484) #published version of preprints before 31 Jan
# rob_records <- rob_records %>%
#   filter(record_id %in%  pub_preprints | record_id <= 5296)

published_preprints <-c(5565,6219, 6685, 7030, 7465, 8249, 9442, 9484)
#include additional study identified from ref list
additional <- 11099
rob_records <- rob_records %>%
  filter(record_id <= 5296 |
           record_id %in% published_preprints |
           record_id %in% additional)
